Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Power Spectra

### 2025-06-18 paper/main.tex
passing back to Steve

Upon obtaining the posterior means from each of the 111 training cosmologies, this 
section details our second contribution - the use of the Bayesian DGP.FCO model 
to predict the curve for held-out cosmologies. This is achieved with modeling the 
weights of different basis functions as GPs.

>>>>

Here we detail our second contribution - using the Bayesian DGP.FCO model predictions
from training cosmologies to predict the matter power spectra for held-out cosmologies. 
%This is achieved with modeling the weights of different basis functions as GPs.
